BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-11-30 tex/4-techniques.tex
Grammar and typos.

This section gives an overview of different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture with then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case. Finally we will talk about deployement to scalable, fault resilient distributed architecture.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}
% Introduction
JavaScript is a widely used use language for client-side web scripting. While some applications simply use it for aesthetics (menus, animations...), an increasing number of websites use JavaScript to download and display content. In such cases, traditional HTML based crawled do not see web pages as they would be presented to a human visitor and might therefore be obsolete for data extraction.

@@

% The solution
To support blogs with JavaScript generated content we embed a full web browser into the crawler. After considering multiple option, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities. The JavaScript rendering is done as the very first step of web page processing. Extracting blog post content, comments or images therefore works equally well on both blogs with JavaScript generated content and traditional HTML-only blogs.

@@

Our crawler is built on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling. Scrapy provide an elegant and modulable architecture illustrated in Figure~\ref{architecture}. Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downleader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog. After downloading its HTML\TODO{rephrase!}, a web page is packed into an \emph{Item} and sent through the following pipeline of operation:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download images
  \item Propagate resulting records to the Invenio back-end
\end{enumerate}
This pipeline design, often called \emph{pipes and filters pattern} \cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity. Indeed, disabeling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}
% Into, blog-post identification
In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner. The \emph{blog-post identification} function is able to identify from a URL whether or not the corresponding page is a blog-post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

% download priority heuristic
In order to efficiently deal with blogs with a large number non-blog-post pages, this blog-post identification mechanism is not sufficient. Indeed, after all pages identified as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts. To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm. Given an URL, the machine learning system does an estimation on the number of links to blog-post the corresponding page will contain. This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visite next. Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data that will then be taken it into account during future predictions. This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.

@@

At the time of writing we did not had the chance to work on a distributed deployment of the BlogForever project. However, the BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, where designed to be usable as part of a event-driven, scalable and fault resilient distributed system.

@@

Scalability and fault resilience are induced by the fact that both \emph{NewCrawl} and \emph{UpdateCrawl} are from a high level viewpoint stateless entities. \emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog-posts, comments and medias. Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{noteC} and a time, and returns records of objects that where emitted after the given time. The absence of state implies that in a distributed setup, crawler instances could be removed, added, and used interchangeably. Regarding the asynchronous architecture, Scrapy is build upon Twisted\cite{twisted2013}, an event-driven networking framework for Python. Scrapy also provides a built-in service to start spiders with an HTTP JSON API. With these tools in hand, the only component to implement in order to achieve a scalable and fault resilient distributed crawling system is an entity to keep track of available crawlers and does appropriate load balancing between them.

>>>>

This section gives an overview of different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture will then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case. Finally we will talk about deployement to scalable, fault resilient distributed architecture.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}
% Introduction
JavaScript is a widely used language for client-side web scripting. While some applications simply use it for aesthetics (menus, animations...), an increasing number of websites use JavaScript to download and display content. In such cases, traditional HTML based crawled do not see web pages as they would be presented to a human visitor and might therefore be obsolete for data extraction.

@@

% The solution
To support blogs with JavaScript generated content, we embed a full web browser into the crawler. After considering multiple option, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities. The JavaScript rendering is done as the very first step of web page processing. Extracting blog post content, comments or images therefore works equally well on both blogs with JavaScript generated content and traditional HTML-only blogs.

@@

Our crawler is built on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling. Scrapy provide an elegant and modulable architecture illustrated in Figure~\ref{architecture}. Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog. After downloading its HTML\TODO{rephrase!}, a web page is packed into an \emph{Item} and sent through the following pipeline of operation:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download medias
  \item Propagate resulting records to the Invenio back-end
\end{enumerate}
This pipeline design, often called \emph{pipes and filters pattern} \cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity. Indeed, disabeling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}
% Into, blog-post identification
In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog-post identification} function is able to identify from an URL whether or not the corresponding page is a blog-post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used to identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

% download priority heuristic
In order to efficiently deal with blogs with a large number of non-blog-post pages, this blog-post identification mechanism is not sufficient. Indeed, after all pages identified as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts. To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm. Given an URL, the machine learning system does an estimation on the number of links to blog-post the corresponding page will contain. This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visite next. Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data that will then be taken into account during future predictions. This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.

@@

At the time of writing we did not had the chance to work on the deployment of the BlogForever project on a distributed environment. However, the BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, where designed to be usable as part of an event-driven, scalable and fault resilient distributed system.

@@

Scalability and fault resilience are induced by the fact that both \emph{NewCrawl} and \emph{UpdateCrawl} are from a high level viewpoint stateless entities. \emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog-posts, comments and medias. Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{noteC} and a time, and returns records of objects that where emitted after the given time. The absence of state implies that in a distributed setup, crawler instances could be removed, added, and used interchangeably.

Regarding the asynchronous architecture, Scrapy is build upon Twisted\cite{twisted2013}, an event-driven networking framework for Python. Scrapy also provides a built-in service to start spiders with an HTTP JSON API. With these tools in hand, the only component to implement in order to achieve a scalable and fault resilient distributed crawling system is an entity to keep track of available crawlers and does appropriate load balancing between them.

### 2013-11-30 tex/5-evaluation.tex
Grammar and typos.

Our evaluation will be articulated in two parts. Firstly, we will compare the content extraction procedure presented in section \ref{algorithms} with three open source projects capable of generically extract content from web articles. The comparison will show that our blog targeted solution has better performances both in term of running time and success rates. Secondly, a discussion will be held regarding the different solutions available to archive data beyond what is available in HTML source code. Extraction of authors, dates and comments is not part of evaluation because of the lack of publicly available competing projects and reference data sets.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction Precision}
To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}. Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, extract it's main textual content. These projects are more generic than our blog specific approach in the sense that they do not make use of web feeds and do not exploit structural similarities of pages of a blog (assuptions \ref{havefeedAssum} and \ref{similarhtmlAssum}). Readability works by .... Boilerpipe uses a very .... Goose implements a more sofisticated algorithm which ....

@@

% rsetup (single core, gc disabled, measure time spent in respective extraction functions)
% result (plot)
\input{runningtimesfigure.tex}

>>>>

Our evaluation will be articulated in two parts. Firstly, we will compare the content extraction procedure presented in section \ref{algorithms} with three open source projects capable of generically extracting content from web articles. The comparison will show that our blog targeted solution has better performances both in term of running time and success rates. Secondly, a discussion will be held regarding the different solutions available to archive data beyond what is available in HTML source code. Extraction of authors, dates and comments is not part of evaluation because of the lack of publicly available competing projects and reference data sets.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction Precision}
To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}. These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (assuptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).

Readability relies mainly on common naming practices among web-developers  .

Boilerpipe uses a very ....
% Boilerpipe is probably one of the best open source packages when it comes to full article text extraction that leverages on machine learning. The overall algorithm works by computing both text and structural features on parts of the document and based on these features, decide if the observed part of the document belongs to the article text or not. The decision rules are inferred by a classifier trained on a set of labeled documents.
% To obtain a set of learning examples that are fed into a classifier, boilerplate observes a list of features on different levels of the HTML document:

% text frequency in the whole corpus: to obtain phrases commonly used in useless parts of the document
% presence of particular tags that enclose a block of text: <h#> headline, <p> paragraph, <a> anchor and <div> division
% shallow text features: average word length, average sentence length, absolute number of words in the segment
% local context of text: absolute and relative position of the text block
% heuristic features: number of words that start with an uppercase letter, number of words written in all-caps, number of date and time tokens, link density and certain ratios of those previously listed
% density of text blocks: number of words in a wrapped fixed column width text block divided by number of lines of the same block
% Each HTML document is segmented into atomic text blocks that are annotated with features listed above and labeled (by a human annotator) with content or boilerpate class.

% In the original paper authors used decision trees and SVMs, trained on previously mentioned set of learning examples, to classify parts of the newly observed document as content or boilerplate text.

Goose implements a more sofisticated algorithm which ....
% clusters of paragraphs, word dencity and link dencity

@@

Implemented in Javascript, Java and Scala respectively, all three offer the same functionality: given an HTML web page, identify and extract content, tit.
% rsetup (single core, gc disabled, measure time spent in respective extraction functions)
% result (plot)
\input{runningtimesfigure.tex}
